---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

---

# (a) Brief Summary

In this talk, Cem Vardar shares his journey from an Industrial Engineering background at METU to leading data science teams at Carvana. He explains that data science should not be seen as a completely separate discipline, but rather as a powerful tool that engineers can use to solve complex system problems.

A key concept he highlights is **evolutionary design**. Instead of replacing systems completely with new solutions, he suggests starting with simple improvements and allowing systems to evolve gradually over time.

He also emphasizes the **80/20 rule (Pareto principle)** in skill development. According to this idea, learning a small but important part of a technical tool such as SQL can provide most of its practical value in real-world applications.

Overall, the talk underlines the importance of **analytical thinking, problem solving, and understanding complex systems** rather than constantly chasing the newest technologies.

---

# Questions & Answers

## Open-Ended Question

**Question**

Cem Vardar mentions that simple solutions are often preferred over complex ones. Why does he advocate an evolutionary approach instead of designing a perfect system from scratch?

**Answer**

Complex systems are influenced by many interacting factors such as human behavior, operational constraints, and organizational culture. Designing a perfect system from scratch often relies on unrealistic assumptions. An evolutionary approach allows engineers to gradually improve the system while observing how each change affects performance.

---

## Multiple Choice Question

**Question**

According to Cem Vardar, which technical tool has remained a constant must-have throughout his career?

A) Deep Learning Frameworks  
B) SQL  
C) Natural Language Processing  
D) Discrete Event Simulation  

**Correct Answer:** **B) SQL**

---

# (b) Data Analysis with R

## Load the dataset

```{r}
library(dslabs)

data("polls_us_election_2016")
data <- polls_us_election_2016
```

## Define personal variables

```{r}
my_first <- "Sena"
my_birth_year <- 2002

k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

## Display rows of the dataset

```{r}
if (k %% 2 == 0) {
  head(data, k)
} else {
  tail(data, k)
}
```

## Count total missing values

```{r}
sum(is.na(data))
```

## Count missing values by column

```{r}
na_counts <- sort(colSums(is.na(data)), decreasing = TRUE)
head(na_counts, 8)
```

## Replace missing values

```{r}
new_data <- data

for (col in names(new_data)) {

  if (is.numeric(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k

  } else if (inherits(new_data[[col]], "Date")) {
    new_data[[col]][is.na(new_data[[col]])] <- as.Date("2002-01-19")

  } else if (is.factor(new_data[[col]])) {
    new_data[[col]] <- as.character(new_data[[col]])
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)

  } else if (is.character(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
  }

}
```

## Display rows of the cleaned dataset

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

## Check remaining NA values

```{r}
sum(is.na(new_data))
anyNA(new_data)
```

---

# Conclusion

After replacing the missing values according to the specified rules, the dataset no longer contains any missing values. The final check using `anyNA()` confirms that the data frame is fully cleaned.

